Estimating Predictive Rate-Distortion Curves via Neural Variational Inference

### 2019-06-17 paper.tex
Updates from Overleaf

@@

\begin{figure*}
\centering
\includegraphics[width=0.45\textwidth]{code/figures/even-info-varyM.pdf}

%\includegraphics[width=0.45\textwidth]{code/figures/even-beta-mem.pdf}
	\caption{Rate-Distortion for the Even Process (left) and the Random Insertion Process (right), varying $M=5$ (blue), $10$ (red), $15$ (green). Gray lines: Analytical curves. Red dots: Multiple runs of NPRD. Red line: Tradeoff curve computed from NPRD runs. Compare Figure~\ref{fig:even} for results from full NPRD.}\label{fig:samples-ptb}
\end{figure*}

>>>>

On English word-level modeling, training took a median number of 9 epochs (max 467 epochs) and 5 minutes (max 126 minutes).

@@

\begin{figure*}
\centering
within minutes after the stock market closed friday , i called sen. bill bradley of new
\includegraphics[width=0.95\textwidth]{code/nprd/figures/sample_0.png}

asset you own would be worth more if the government suddenly announced that if you sold
\includegraphics[width=0.95\textwidth]{code/nprd/figures/sample_20.png}

, OOV the office of richard darman , director of the office of management and budget
\includegraphics[width=0.95\textwidth]{code/nprd/figures/sample_13.png}

he thinks , when the white house is forced to ask for higher taxes to meet
\includegraphics[width=0.95\textwidth]{code/nprd/figures/sample_31.png}

	\caption{}\label{fig:samples-ptb}
\end{figure*}
